### 2021-05-20 written/eLifeRevision/Bittner_eLife2020.tex
V1 fig and other captions

For comparison, we infer the parameters $\mathbf{z}$ likely to produce stable amplification using two alternative simulation-based inference approaches.
Sequential Monte Carlo approximate bayesian computation (SMC-ABC) \cite{sisson2007sequential} is a rejection sampling approach that uses SMC techniques to improve efficiency, and sequential neural posterior estimation (SNPE) \cite{gonccalves2019training} approximates posteriors with deep probability distributions (see Section \ref{methods_related}).
Unlike EPI, these statistical inference techniques do not constrain the statistics of the predictive distribution, so they were run by conditioning on an exemplar dataset  $\mathbf{x}_0 = \bm{\mu}$, following standard practice with these methods \cite{sisson2007sequential, gonccalves2019training}.
To compare the efficiency of these different techniques, we measured the time and number of simulations necessary for the distance of the predictive mean to be less than 0.5 from $\bm{\mu} = \mathbf{x}_0$ (see Section \ref{methods_RNN}).

@@

\q{v1_ep_text1}{We quantify levels of E-population variability by studying two emergent properties}
\begin{equation}\label{eq:EP_V1}
\begin{split}
\mathcal{X}(5\text{Hz}) ~~:~~  \mathbb{E}_{\mathbf{z}}\begin{bmatrix} s_E(\mathbf{x}; \mathbf{z}) \end{bmatrix}  &~~=~~ 5\text{Hz}~~~~~~~\mathcal{X}(10\text{ Hz}) ~~:~~  \mathbb{E}_{\mathbf{z}}\begin{bmatrix} s_E(\mathbf{x}; \mathbf{z}) \end{bmatrix}  ~~=~~ 10\text{Hz}  \\ 
 \text{Var}_{\mathbf{z}}\begin{bmatrix} s_E(\mathbf{x}; \mathbf{z}) \end{bmatrix}  &~~=~~  1 \text{Hz}^2~~~~~~~~~~~~~~~~~~~~~~~ \text{Var}_{\mathbf{z}}\begin{bmatrix} s_E(\mathbf{x}; \mathbf{z}) \end{bmatrix}  ~~=~~  1 \text{Hz}^2,
\end{split}
\end{equation}
\q{v1_ep_text2}{where $s_E(\mathbf{x}; \mathbf{z})$ is the standard deviation of the stochastic $E$-population response about its steady state (Fig. \ref{fig:V1}C).
In the following analyses, we select 1Hz$^2$ variance such that the two emergent properties do not overlap in $s_E(\mathbf{z}; \mathbf{x})$.}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.75]{figures/fig4/fig4.pdf}
\end{center}
\vspace{-.25cm}
\caption{\small
\textbf{A}. Rapid task switching behavioral paradigm (see text). 
\textbf{B}. Model of superior colliculus (SC). Neurons: LP - Left Pro, RP - Right Pro, LA - Left Anti, RA - Right Anti. 
Parameters: $sW$ - self, $hW$ - horizontal, $vW$ -vertical, $dW$ - diagonal weights.  
\textbf{C}. The EPI inferred distribution of rapid task switching networks.  
Red/purple parameters indicate modes $\mathbf{z}^*(sW)$ colored by $sW$.
Sensitivity vectors $\mathbf{v}_1(\mathbf{z}^*)$ are shown by arrows.
(Bottom-left) EPI predictive distribution of task accuracies.
\textbf{D}. Mean and standard error ($N_{\text{test}}$ = 25) of accuracy in Pro (top) and Anti (bottom) tasks after perturbing connectivity away from mode along $\mathbf{v}_1(\mathbf{z}^*)$ (left), $\mathbf{v}_{\text{task}}$ (middle), and $\mathbf{v}_{\text{diag}}$ (right).
}
\label{fig:SC}
\end{figure}

@@

Circuit responses are simulated using $T = 200$ time steps at $dt = 0.5\text{ms}$ from an initial condition drawn from $\mathbf{x}(0) \sim U\left[10\text{ Hz}, 25\text{ Hz}\right]$.
Standard deviation of the E-population $s_E(\mathbf{x}; \mathbf{z})$ is calculated as the square root of the temporal variance from $t_{ss} = 75\text{ms}$ to $Tdt = 100\text{ms}$ averaged over 100 independent trials.
\begin{equation}
s_E(\mathbf{x}; \mathbf{z}) =\mathbb{E}_{x}\left[\sqrt{\mathbb{E}_{t > t_{ss}}\left[\left(x_E(t) -\mathbb{E}_{t > t_{ss}}\left[ x_E(t) \right]\right)^2 \right]}\right]
\end{equation}

@@

\begin{figure}[h]
\caption{EPI inferred distribution for $\mathcal{X}(10\text{ Hz})$.
 }
 \label{fig:V1_1}
\begin{center}
\includegraphics[scale=.8]{figures/figV1_3/figV1_3.pdf}
\end{center}
\end{figure}

\begin{figure}[h]
\caption{EPI optimization $q_{\bm{\theta}}(\mathbf{z} \mid \mathcal{X}(5\text{ Hz}))$
\textbf{A}. Entropy throughout optimization. 
\textbf{B}. The emergent property statistic means and variances converge to their constraints at 8,000 iterations following the fourth augmented lagrangian epoch.
 }
 \label{fig:V1_2}
\begin{center}
\includegraphics[scale=.8]{figures/figV1_4/figV1_4.pdf}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=1.]{figures/figSC2/figSC2.pdf}
\end{center}
\caption{
\textbf{A}. Simulations in network regime 1 ($hW_{\text{fixed}} = -1.5$).
\textbf{B}. Simulations in network regime 2 ($hW_{\text{fixed}} = -1.5$) .
}
\label{fig:SC2}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{figures/figSC7/figSC7.pdf}
\end{center}
\caption{
\textbf{A}. Entropy throughout optimization. 
\textbf{B}. The emergent property statistic means and variances converge to their constraints at 20,000 iterations following the tenth augmented lagrangian epoch.
}
\label{fig:SC7}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.8]{figures/figSC8/figSC8.pdf}
\end{center}
\caption{
\textbf{A}. Entropy throughout optimization. 
\textbf{B}. The emergent property statistic means and variances converge to their constraints at 20,000 iterations following the tenth augmented lagrangian epoch.
}
\label{fig:SC8}
\end{figure}

>>>>

For comparison, we infer the parameters $\mathbf{z}$ likely to produce stable amplification using two alternative simulation-based inference approaches.
Sequential Monte Carlo approximate bayesian computation (SMC-ABC) \cite{sisson2007sequential} is a rejection sampling approach that uses SMC techniques to improve efficiency, and sequential neural posterior estimation (SNPE) \cite{gonccalves2019training} approximates posteriors with deep probability distributions (see Section \ref{methods_related}).
Unlike EPI, these statistical inference techniques do not constrain the predictions of the inferred distribution, so they were run by conditioning on an exemplar dataset  $\mathbf{x}_0 = \bm{\mu}$, following standard practice with these methods \cite{sisson2007sequential, gonccalves2019training}.
To compare the efficiency of these different techniques, we measured the time and number of simulations necessary for the distance of the predictive mean to be less than 0.5 from $\bm{\mu} = \mathbf{x}_0$ (see Section \ref{methods_RNN}).

@@

\q{v1_ep_text1}{We quantify levels of E-population variability by studying two emergent properties}
\begin{equation}\label{eq:EP_V1}
\begin{split}
\mathcal{X}(5\text{Hz}) ~~:~~  \mathbb{E}_{\mathbf{z}}\begin{bmatrix} s_E(\mathbf{x}; \mathbf{z}) \end{bmatrix}  &~~=~~ 5\text{Hz}~~~~~~~\mathcal{X}(10\text{Hz}) ~~:~~  \mathbb{E}_{\mathbf{z}}\begin{bmatrix} s_E(\mathbf{x}; \mathbf{z}) \end{bmatrix}  ~~=~~ 10\text{Hz}  \\ 
 \text{Var}_{\mathbf{z}}\begin{bmatrix} s_E(\mathbf{x}; \mathbf{z}) \end{bmatrix}  &~~=~~  1 \text{Hz}^2~~~~~~~~~~~~~~~~~~~~~~~ \text{Var}_{\mathbf{z}}\begin{bmatrix} s_E(\mathbf{x}; \mathbf{z}) \end{bmatrix}  ~~=~~  1 \text{Hz}^2,
\end{split}
\end{equation}
\q{v1_ep_text2}{where $s_E(\mathbf{x}; \mathbf{z})$ is the standard deviation of the stochastic $E$-population response about its steady state (Fig. \ref{fig:V1}C).
In the following analyses, we select 1Hz$^2$ variance such that the two emergent properties do not overlap in $s_E(\mathbf{z}; \mathbf{x})$.}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.75]{figures/fig4/fig4.pdf}
\end{center}
\vspace{-.25cm}
\caption{\small
\textbf{A}. Rapid task switching behavioral paradigm (see text). 
\textbf{B}. Model of superior colliculus (SC). Neurons: LP - Left Pro, RP - Right Pro, LA - Left Anti, RA - Right Anti. 
Parameters: $sW$ - self, $hW$ - horizontal, $vW$ -vertical, $dW$ - diagonal weights.  
\textbf{C}. The EPI inferred distribution of rapid task switching networks.  
Red/purple parameters indicate modes $\mathbf{z}^*(sW)$ colored by $sW$.
Sensitivity vectors $\mathbf{v}_1(\mathbf{z}^*)$ are shown by arrows.
(Bottom-left) EPI predictive distribution of task accuracies.
\textbf{D}. Mean and standard error ($N_{\text{test}}$ = 25, bars not visible) of accuracy in Pro (top) and Anti (bottom) tasks after perturbing connectivity away from mode along $\mathbf{v}_1(\mathbf{z}^*)$ (left), $\mathbf{v}_{\text{task}}$ (middle), and $\mathbf{v}_{\text{diag}}$ (right).
}
\label{fig:SC}
\end{figure}

@@

Circuit responses are simulated using $T = 200$ time steps at $dt = 0.5\text{ms}$ from an initial condition drawn from $\mathbf{x}(0) \sim U\left[10\text{Hz}, 25\text{Hz}\right]$.
Standard deviation of the E-population $s_E(\mathbf{x}; \mathbf{z})$ is calculated as the square root of the temporal variance from $t_{ss} = 75\text{ms}$ to $Tdt = 100\text{ms}$ averaged over 100 independent trials.
\begin{equation}
s_E(\mathbf{x}; \mathbf{z}) =\mathbb{E}_{x}\left[\sqrt{\mathbb{E}_{t > t_{ss}}\left[\left(x_E(t) -\mathbb{E}_{t > t_{ss}}\left[ x_E(t) \right]\right)^2 \right]}\right]
\end{equation}

@@

\begin{figure}[h]
\caption{EPI inferred distribution for $\mathcal{X}(10\text{Hz})$.
 }
 \label{fig:V1_1}
\begin{center}
\includegraphics[scale=.8]{figures/figV1_3/figV1_3.pdf}
\end{center}
\end{figure}

\begin{figure}[h]
\caption{EPI optimization $q_{\bm{\theta}}(\mathbf{z} \mid \mathcal{X}(5\text{Hz}))$
\textbf{A}. Entropy throughout optimization. 
\textbf{B}. The emergent property statistic means and variances converge to their constraints at 8,000 iterations following the fourth augmented lagrangian epoch.
 }
 \label{fig:V1_2}
\begin{center}
\includegraphics[scale=.8]{figures/figV1_4/figV1_4.pdf}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=1.]{figures/figSC2/figSC2.pdf}
\end{center}
\caption{
\textbf{A}. Simulations in network regime 1: $\mathbf{z}^*(sW=-0.75)$.
\textbf{B}. Simulations in network regime 2: $\mathbf{z}^*(sW=0.75)$.
}
\label{fig:SC2}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{figures/figSC7/figSC7.pdf}
\end{center}
\caption{EPI optimization of the SC model producing rapid task switching.
\textbf{A}. Entropy throughout optimization. 
\textbf{B}. The emergent property statistic means and variances converge to their constraints at 20,000 iterations following the tenth augmented lagrangian epoch.
}
\label{fig:SC7}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.8]{figures/figSC8/figSC8.pdf}
\end{center}
\caption{
\textbf{A}.Rapid task switching SC connectivities obtained from random sampling.
\textbf{B}. Task accuracies of the inferred distributions from random sampling (top) and EPI (bottom).
}
\label{fig:SC8}
\end{figure}
